Inefficient Concessions and Mediation

### 2021-02-18 draft.tex
clean up notes for JCR submission; fix one typo in draft

\begin{theorem}
	When concessions have future material value, the mediation mechanism $M$ can be used to
	\begin{enumerate}
		\item[(a)] improve welfare by increasing the efficiency of concessions when only a \emph{concessions separating equilibrium with inefficient gifts} is possible; or
		\item[(b)] improve welfare despite reducing the efficient of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
		\item[(c)] achieve peace when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.
	\end{enumerate}
	\label{theorem:medwel}
\end{theorem}
\emph{Proof:} See Appendix.

>>>>

\begin{theorem}
	When concessions have future material value, the mediation mechanism $M$ can be used to
	\begin{enumerate}
		\item[(a)] improve welfare by increasing the efficiency of concessions when only a \emph{concessions separating equilibrium with inefficient gifts} is possible; or
		\item[(b)] improve welfare despite reducing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
		\item[(c)] achieve peace when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.
	\end{enumerate}
	\label{theorem:medwel}
\end{theorem}
\emph{Proof:} See Appendix.
